Comparative Analysis of the wav2vec 2.0 Feature Extractor

### 2023-02-27 main.tex
FE dedicated command

\begin{abstract}
\end{abstract}
\noindent\textbf{Index Terms}: speech recognition, feature extraction, raw waveform modeling

>>>>

\begin{abstract}
Raw waveform modeling is an interesting research topic for \gls{ASR}.
\wvtwo has seen large success recently and makes use of a convolutional \fe which operates directly on the speech waveform.
Typically, this \fe is seen as part of the overall architecture, but this work investigates this component specifically.
It is used as a replacement for classical feature extraction methods in a \gls{CTC} setup and compared to an alternative neural \fe approach.
Finally, we analyze the learned representations of both neural \fes.
\end{abstract}
\noindent\textbf{Index Terms}: speech recognition, feature extraction, raw waveform modeling
